\documentclass{article}

\usepackage{constitutional}

\title{Constitution Notes}
\newcommand{\nation}{The Nation}

\begin{document}
    \maketitle
    \section*{General Design}
    This Constitution aims to tackle some problems in modern democracy:
    \begin{itemize}
        \item Voter Apathy

            Make voters feel as though they have a direct impact in elections
        \item Voter Turnout

            Connected to voter apathy. Ideally, all elligible citizens should
            vote. Additionally, the right of suffrage should be extended to
            broad portions of the population.
        \item Powerful Rights

            Rights are added to this Constitution under the belief that they
            are general enough to be desired by any population. If a right
            is variable, such that it depends on age or some other factor, it
            is possibly best implemented through normal legislation.
        \item Accessible

            This Constitution should be easy to understand.
    \end{itemize}

    \section*{To Do}

    There are several portions of this Constitution that are underdeveloped and
    could use improvement.

    \subsection*{Martial Law}
    \subsection*{Rule of Law}

    \subsection*{Preamble}

    The Preamble sets the spirit of the rest of the document. As part of this
    it needs to establish a source of government legitimacy, touch on national

    values, and announce the goals of the Constitution. It needs to do all this
    while being simple enough for the average person to memorize so that it
    forms the emotional connection between the laws of the nation and the people
    of the nation.

    It's likely that due to the cultural nature of the above requirements, this
    Preamble would have to be completely re-written for any population looking
    to adopt this Constitution. Nevertheless, a reasonable attempt should be
    made.

    \subsection*{Executive Power}

    What is the relationship between the President, the military, and the
    diplomatic service? What portions of the bureaucracy are controlled by the
    President, and what's controlled by the Prime Minister?

    \subsection*{Proportional Voting}

    The general idea is that the legislature is a mixed-member, parliamentary,
    unicameral system. These words should never show up in the Constitution -
    the legislative system should be described in an unambiguous and easy-to-
    understand way.

    \subsection*{Full Faith and Credit}

    Integrate the American concept of "full faith and credit" between the
    states. This is necessary because it leads \nation{} to behaving more like
    a single country instead of a collection.

    Full faith and credit can lead to problems where states impose undesired
    laws and rights on other states. Certain things should be made the purview
    of the national government, such as patents and currency. In general, the
    supremacy of Parliament over the states should help address this issue.

    \subsection*{Eliminate Latin Phrases and English Precedent/Common Law}

    This is supposed to be a very general document, acceptable to most people
    on the planet. As such, it should be accessible and understandable to most
    people on the planet.

\end{document}
