\documentclass{report}

\usepackage{constitutional}

\title{Constitution}
\newcommand{\nation}{The Nation}

\begin{document}
    \maketitle
    \section{Preamble}
    The goal of this document is to establish a democratically elected government,
    whose purpose is to provide for the welfare, defense, and justice of \nation.
    This government shall operate under the rule of law and protect the rights of
    the people

    \section{Article 1}

    Parliament is granted all legislative powers of \nation, and shall be made
    up of 125 Representatives.

    Sixty-two Representatives are elected in local districts using instant-runoff
    voting. Sixty-three Representatives are selected by the parties in a
    mixed-member voting system.

    A Parliamentary election is triggered by a simple majority vote in Parliament
    or when 5 years have passed since the previous election. After each election,
    if a single party has a majority in Parliament, it forms the Government. If
    no single party has a majority, a number of parties necessary to possess a
    majority must join together to form a coalition Government. If the Government
    cannot be formed, another election is held.

    Each time an election is held and a Government is formed, the Government
    elects, from among its Representatives, a single person to appoint as the
    Prime Minister. The Prime Minister may then choose Ministers from all the
    elected Representatives to head the executive offices of the state.

    Parliament must assemble for session at least once a year, and a majority of
    Representatives must be present in order to constitute a quorum. If the
    annual budget or issues related to national security, territorial integrity,
    and national sovereignty are under discussion, Parliament may not recess
    until the matter is decided.

    A Representative must be a citizen of \nation{} for at least seven years and
    be at least 25 years old. If a Representative is elected for an electoral
    district, they must be a resident of the district for which they are
    elected. No person may simultaneously be a Representative and the President
    or a Justice of a court.

    Parliament may, by a simple majority vote and pending signature by the
    President, establish taxes and tariffs, declare war, provide for the
    funding of the bureaucracy and salaries for public office holders, and pass
    any laws or acts necessary to fulfill any functions of the state. The
    salaries of public office holders shall not be increased during a term in
    office.

    Parliament may, by a simple majority vote, approve treaties negotiated and
    submitted by the President. After being approved by Parliament, the
    President may sign the treaty into law or veto.

    Parliament may not pass ex post facto legislation nor bills of attainder.

    Parliament may, by a simple majority vote, establish rules governing the
    procedures of Parliament.

    Parliament may, by a simple-majority vote and pending signature by the
    President, repeal previously passed legislation.

    Parliament may, by a two-thirds majority vote and pending signature by
    the President, modify the rules governing the process for naturalizing new
    citizens.

    Parliament may, by a three-fourths majority vote, remove the President or a
    court Justice from office.

    \section{Article 2}

    The executive office is held by a President, who is reponsible for
    representing \nation{} to foreign governments.

    The President has the sole power to pardon those convicted of a criminal
    offense or commute their sentences, and vto or sign legislation passed by
    Parliament. Any legislation that isn't vetoed by the President within 7 days
    is considered signed and approved.

    Pending majority approval by Parliament, the President has the sole power
    to appoint Justices to the Supreme Court and other national courts as well
    as appoint ambassadors.

    The President may summon Parliament to hold an emergency session and present
    matters to discuss to Parliament.

    The President may announce a Parliamentary election no sooner than one year
    after the previous Parliamentary or Presidential election.

    The President is the Commander in Chief of the military, and may exercise
    those powers in times of war or should the sovereignty or territorial
    integrity of \nation{} come under attack.

    The President must be a citizen of the nation for at least 10 years and be
    at least 35 years old. No person may hold the office of the President for
    more than three terms. The President must reject and renounce the titles,
    offices, and citizenships of any foreign states or nations. They must also
    reject any gifts from foreign states or nations that aren't purely
    cermonial in nature. The President may not be a Representative nor a court
    Justice while holding the office of the Presidency.

    Presidential elections are held every five years and begin on the first
    Saturday in the month of December and continue into the following Sunday.
    Presidential elections use instant-runoff voting.

    On the first day of the first year after an election, the President-Elect
    takes the oath of office and is sworn in by the Chief Justice of the
    Supreme Court.

    In the case of a vacancy of the Presidency, the office will be filled by the
    next available person in a line of succession that begins with the Prime
    Minister, then the Cabinet Ministers, and then the Representatives in
    Parliament. The order in which members and Representatives are
    chosen is done in a manner set by law.

    \section{Article 3}

    The Supreme Court is made up of fifteen Justices, and has original
    jurisdiction in all cases where \nation{} is defending, and all cases
    concerning ambassadors and members of the diplomatic service.

    The Supreme Court has appellate jurisdiction above any other courts
    established by Parliament. Parliament may assign new jusidictions to the
    Supreme Court and any national courts, so long as they do not conflict with
    this Constitution.

    The Supreme Court has appellate jurisdiction over the supreme courts of the
    provinces.

    The Supreme Court has the power to rule a law as violating this Constitution
    should the law be challenged in court.

    Justices to the Supreme Court must be at least 40 years old and have been a
    citizen for ten years or more. Justices serve for twenty years or until they
    retire. Justices may not be appointed to the Supreme Court more than once.

    Justices to the Supreme Court and any other national court are entitled to
    periodic compensation that may not be decreased during their tenure.

    \section{Article 4}

    This Constitution recognizes and protects certain rights to all citizens of
    the nation and to all people. No legislation passed by Parliament or any of
    the provinces may violate or infringe upon these rights, and their
    enumeration does not preclude the existence of others.

    \subsection{Freedom of Speech}

    The State may not limit the freedom of speech, association, press, or
    peaceable assembly, nor may the State establish or support any religion.

    The free exercise of religion may only be restricted to protect the health
    and safety of the individual.

    \subsection{Privacy}

    Individuals have the right to protection from undue intrusion into their solitude
    and personal lives, as well as the public disclosure of embarassing private facts.

    \subsection{Search and Seizure}

    In order for a person's body, belongings, or property to be searched, a
    specific warrant must be issued by a court with jurisdiction over the case.

    \subsection{Integrity of Body}

    No person may be subjected to cruel, unusual, or degrading treatment or
    punishment. No person may be subjected to torture by the State, nor is
    information obtained through torture admissable in court.

    \subsection{Prohibition of Slavery}

    All slavery and human trafficking is prohibited. Slavery includes labor
    that is compensated so little as to be grossly insufficient to support
    life.

    \subsection{Non-Discrimination}

    No government may not discriminate based on sex, gender, religion, race, color,
    ethnicity, ideology, disability, or sexual orientation.

    \subsection{Due Process}

    In any criminal or civil case, the accused has the right to know their
    accuser and the accusation, and the right to a speedy and public trial by
    a jury of their peers.

    No person may be put on trial for the same crime more than once. In all
    criminal prosecutions, the accused has the right to legal counsel in their
    defense.

    No person may be tried for a capital or otherwise infamous crime without
    the presentation of the case to a Grand Jury.

    Any person accused of a crime is presumed innocent until proven guilty
    under the law.

    \subsection{Right to Vote}

    Every citizen of \nation{} that is at least eighteen years old may vote in
    national elections and elections for the province and disctrict in which
    they reside. The right to vote may not be limited by any fee or test.

    \subsection{Access to Documents}

    Every citizen of \nation{} has the right to access the documents and
    reasoning of Parliament, the Judiciary, and the State.

    \subsection{Education}

    Every citizen of \nation{} has the right to an effective and thorough
    education. Parents have the right to oversee their child's education, and
    all citizens have the right to establish their own educational institutions.

    \subsection{Conduction of Business}

    All people have the right to conduct lawful business free from discrimination.

\end{document}
